### 2020-02-21 README.Rmd
Fixed S3 generic consistency issues, ref #15

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
<!-- badges: end -->

The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia. It is very popular in Taiwan, Japan and Hong Kong] is to generate and administrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
<!-- badges: end -->

The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia. It is very popular in Taiwan, Japan and Hong Kong. In Cantonese and Taiwanese Mandarin, the same word can also mean "confused". It perfectly captures the spirit of human-in-the-loop validation. ] is to generate and administrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
